Brief notes on erosion

### 2020-08-06 docs/proposals/NSF/budgets/budgetJustUSNA.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (PI: Matthew Moore, co-PI: Bryan
Quaife)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of the
PI's summer salary in each of years 1--3, one month of the co-PI's
summer salary in years 1 and 2, and 0.5 months of the co-PI's summer
salary in year 3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. The PI's monthly salary in
year one is $\$9,720$. The co-PI's monthy salary is $\$10,553$. For
years 2 and 3, a 3\% increase is included.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    PI &    $\$9,720$  & $\$10,012$ & $\$10,312$ & $\$30,044$\\
    \hline
    co-PI & $\$10,553$ & $\$10,869$ & $\$5,598$  & $\$27,020$ \\
    \hline
    Total & $\$20,273$ & $\$20,881$ & $\$15,910$ & $\$57,064$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{B: Other Personnel}
%\hfill \\
%\noindent
The requested other personnel funding includes salary for one full-time
Ph.D.~student in two semesters of each year starting at $\$21,000$.  The
Ph.D.~student will develop and perform numerical simulations. An annual
increase of 3\% is included.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Ph.D. & $\$21,000$ & $\$21,630$ & $\$22,279$ & $\$64,909$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
{\bf PI:} The fringe benefits of the PI are 17.06\%. \\
{\bf co-PI:} The fringe benefits of the co-PI are 17.06\%. \\
{\bf Ph.D.:} The fringe benefits of the graduate student are
0.1\% plus an $\$1,965$ health insurance. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    PI & $\$1,658$ & $\$1,708$ & $\$1,759$ & $\$5,125$ \\
    \hline
    co-PI & $\$1,800$ & $\$1,854$ & $\$955$ & $\$4,609$ \\
    \hline
    Ph.D. & $\$1,986$ & $\$1,987$ & $\$1,987$ & $\$5,960$ \\
    \hline
    Total & $\$5,444$ & $\$5,549$ & $\$4,701$ & $\$15,694$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to fund two total annual domestic trips
for the PI, co-PI, or the Ph.D.~student.  The expected costs per
conference participant is $\$1,750$ with a breakdown of $\$600$ for
airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops.  The PI, co-PI, and Ph.D.~student will
give presentations and actively participate in the meeting or workshop.
Travel funds for the first year are removed due to the COVID crisis
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Conferences &  & $\$3,500$ & $\$3,500$ & $\$7,000$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies is to purchase two $\$1,500$ laptops with accessories, which is
not otherwise available, for the PI, co-PI, and Ph.D.~student in year 1.
The laptops will be used for developing the proposed algorithms and
presenting the results at conferences.  The laptops will give the group
members the flexibility to work on the proposed research remotely.  The
laptops will be used exclusively for the proposed research. 
\\
\paragraph{\bf Other:} The requested other direct costs are to cover the
Ph.D.~student's tuition for 18 credit hours, at a rate of $\$407.55$ per
credit hour in year 1.  An annual increase of 1\% is included per
published university projections.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Materials and Supplies & $\$3,000$ & & & $\$3,000$ \\
    \hline
    Other & $\$7,336$ & $\$7,409$ & $\$7,484$ & $\$22,229$ \\
    \hline
    Total & $\$10,336$ & $\$7,409$ & $\$7,484$ & $\$25,229$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$57,053$ & $\$58,969$ & $\$53,874$ & $\$169,896$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
Florida State University's federally negotiated indirect cost rate is
54\% for research on modified total direct costs (MTDC) which excludes
tuition.  The base for overhead is $\$49,717$ in year 1, $\$51,560$ in
year 2, and $\$46,390$ in year 3.  Florida State University defines a
fiscal year to be July 1--June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$26,847$ & $\$27,842$ & $\$25,051$ & $\$79,740$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$83,900$ & $\$86,811$ & $\$78,925$ & $\$249,636$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of the
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added: \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
    \hline
    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
    \hline
    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10849.85
$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in years 2 and 3.  The expected costs per
conference participant is $\$1,750$ with a breakdown of $\$600$ for
airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops. 
Alternatively, co-PI Moore may use these travel funds to visit PI Quaife and the funded graduate student at FSU in order to collaborate on the project.
Travel funds for the first year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies of \$1000 in year 1 is to partially fund a laptop or desktop computer for co-PI Moore. The computer will be used for developing the proposed algorithms and
presenting the results at conferences.
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,130.92$ & $\$14,374.31$ & $\$14,668.63$ & $\$43,173.86
$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's federally negotiated indirect cost rate is
10\% for research on modified total direct costs (MTDC).
The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
year 2, and $\$14,668.63$ in year 3.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,413.09$ & $\$1,437.43$ & $\$1,466.86$ & $\$4,317.38$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$15,544.01$ & $\$15,811.74$ & $\$16,135.49$ & $\$47,491.24$ \\
    \hline
  \end{tabular}
\end{center}
